---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# vicdffhmap

<!-- badges: start -->
<!-- badges: end -->

***vicdffhmap*** is a simple package containing sf objects for the Victorian Department of Families, Fairness and Housing's divisions and areas.

The Department of Families, Fairness and Housing has four divisions and 17 areas. 

Areas are groups of local government areas. 

Divisions are groups of areas. 

We have used this simple aggregation approach to create sf objects by summarising objects obtained using `strayr::read_absmap("lga2021")`

## Installation

You can install the development version of vicdffhmap from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("zerogetsamgow/vicdffhmap")
```

## division_map

The following plot shows a map of the four divisionss which are contained in `vicdffhmap::division_map`.

```{r division_map}
library(vicdffhmap)

## basic division_map
ggplot2::ggplot(
  division_map,
  ggplot2::aes(
    geometry = geometry,
    fill = division_name,
    label = division_name,
    x = cent_long,
    y = cent_lat
    )
  ) +
  ggplot2::geom_sf(
   colour = vpstheme::bv.smoke
   )+
  ggplot2::geom_label(
    colour = vpstheme::bv.charcoal, 
    fill = "grey", size = ggplot2::unit(7,"pt"))+
  vpstheme::scale_fill_dffh(palette = "core", reverse = TRUE, guide = "none")+
  ggthemes::theme_map()+
  ggplot2::theme(
    legend.position.inside = c(.7,.7)
  )

```



## area_map

The following plot shows a map of the 17 areas which are contained in `vicdffhmap::area_map`

```{r include = FALSE}
north_colours = vpstheme::dffh_colours$tints_purple
names(north_colours) = 
  area_tbl |> 
    dplyr::filter(division_name == "North division") |>
    dplyr::pull(area_name) |> unique()

west_colours = c(vpstheme::dffh_colours$tints_teal,vpstheme::dffh_colours$tints_teal[4])
names(west_colours) = 
  area_tbl |> 
    dplyr::filter(division_name == "West division") |>
    dplyr::pull(area_name) |> unique()

east_colours = c(vpstheme::dffh_colours$tints_green)
names(east_colours) = 
  area_tbl |> 
    dplyr::filter(division_name == "East division") |>
    dplyr::pull(area_name) |> unique()

south_colours = c(vpstheme::dffh_colours$tints_blue)
names(south_colours) = 
  area_tbl |> 
    dplyr::filter(division_name == "South division") |>
    dplyr::pull(area_name) |> unique()

```

```{r area_map}
## basic area_map
ggplot2::ggplot(
  area_map,
  ggplot2::aes(
    geometry = geometry,
    fill = area_name,
    label = area_name,
    x = cent_long,
    y = cent_lat
    )
  ) +
  ggplot2::geom_sf(
   colour = vpstheme::bv.smoke
   )+
  ggrepel::geom_label_repel(
    colour = vpstheme::bv.charcoal, 
    fill = vpstheme::bv.smoke, size = ggplot2::unit(3,"pt"),
    max.overlaps = 20,
    segment.colour = vpstheme::bv.smoke)+
  ggplot2::scale_fill_manual(
    values = c(north_colours, west_colours, east_colours, south_colours), guide = "none")+
  ggthemes::theme_map()+
  ggplot2::theme(
    legend.position.inside = c(.7,.7)
  )

```

## clean_dffh_area()

To assist with joining datasets to the shapefiles, ***vicdffhmap*** exports the `clean_dffh_name()` function. This function will return strings formatted as per the area_name variable in `area_map`. For example:

```{r include = TRUE}

clean_dffh_area("Hume moreland")

clean_dffh_area("NE Melb")

```
The function can also be used to create abbreviated names for each area with 15 or less characters.

## area_tbl

The package contains a third dataset `vicdffhmap::area_tbl` which shows the mapping of local government areas, to areas, to divisions

```{r division_tbl}
## print full table of regions, areas and lgas
knitr::kable(
  area_tbl
)

```
